\chapter{Introduction}

% TODO

Point clouds smoothing is a well-studied problem: numerous methods exists and
have been proven to work more or less nicely on different kinds of data
(presence of noise...). In this report, we want to tackle the problem of
smoothing while preserving informations.

More precisely, given a cloud of points, we want to be able to smooth it by
taking into account the different scales present in it: we want to have a more
important smoothing on large parts of the point set. An example where this kind
of smoothing could be interesting is when we build a 3D scan of an object: we
want to be able to smooth the point cloud while preserving details (the
signature of the author for example).

A lot of smoothing algorithms already exist, some are related to Computer
Vision, some are more based on Computational Geometry techniques:
\begin{itemize}
    \item Gaussian / Laplacian smoothing and all the related filters: adaptive
        filter...
    \item Jet smoothing: a jet is a truncated Taylor expansion. Such jets are
        fitted around points. Jet smoothing operates by projecting the input
        points on an estimated smooth parametric surface (the so-called jet
        surface). Jets are good because they intrinsically contain
        differential information such as normal, curvature...
\end{itemize}

In this report, we will focus on another algorithm which was proposed by
\cite{chambolle2012nonlocal}. Basically, it is a mean curvature flow under an
energy minimization. This energy is related to a non-local curvature.

More formally, let's suppose we have a point cloud in $ \mathbb{R}^d $ made of $
N $ points : $ p_1, \ldots, p_N $, we want to apply an adaptive smoothing on it.
Firstly, we will compute the energy that we want to minimize: $ E(P) = Vol(P + r
K) $ where $ K $ is a chosen convex polyhedron, $ r \in \mathbb{R} $ and $ (+) $ is
the Minkowski sum. If we choose $ K = B(0, 1) $ an euclidean ball, then $ P + rK
$ is the $ r $-offset of P and $ E(P) $ is the volume of a union of balls. In
this case, the $ r $-offset will contain intrinsic informations about the point
set like normal direction or curvature approximation.

Secondly, we will compute the gradient of this energy. For doing that, there are
multiple choices: use analytical formulae (which exist at least in 2D), use
approximations (finite differences) or use a technique called automatic
differentiation that allows use to differentiate any function by changing the
number type and so increasing the complexity a little bit. We will try to use,
in most cases, the automatic differentiation method since it allows us to
have better results than approximate methods without being too painful to
implement.

Finally, we will move our point set in the direction which will be computed as
the result of a gradient descent algorithm applied on the point set. The
weighting will be an important question.

The main problems we will encounter in 3D will be linked to the computation of
Voronoi diagrams for any norms which can be a very difficult thing to do. We
will need to develop techniques in order to properly compute the Voronoi cells
and thus to, in the end, compute the volume of the Minkowski sum of a point
cloud and a convex polyhedron.

The advantage of such algorithm resides in its anisotropy: since the polyhedron
$ K $ may be anything, it can privilege some directions in the space and so
preserve some details.

We will test this algorithm using multiple choices of polyhedrons, values of $ r
$, point sets with a small / high amount of noise to see if the algorithm is
noise-resilient or not.

% vim: set spelllang=en :
